Worflow

### 2017-06-07 R/workflow.Rmd
RSEC no merge but sub and seq

```{r rsec_50}
W <- colData(se)[, grepl('^W', colnames(colData(se)))]
W <- as.matrix(W)
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  print(system.time(ceObj <- RSEC(t(W), k0s = 4:15, 
                                  alphas = c(0.3), betas = c(0.9),
                                  clusterFunction = "hierarchical01",
                                  minSizes = 5,
                                  ncores = NCORES,
                                  combineProportion = 0.7,
                                  mergeMethod = "locfdr",
                                  mergeCutoff = 0.01)))
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

```{r examineCombineMany}
plotClusters(ceObj, colPalette = c(bigPalette, rainbow(100)))
```

@@

FP: Elizabeth, we are working with the W here, does the locfdr make sense in this context?

```{r examineMergeClusters}
#re-does merging simpling to make plot 
mergeClusters(ceObj, mergeMethod = "locfdr",
              plotInfo = "mergeMethod", cutoff = 0.05)
```

@@

```{r compareClusters}
plot(fit$points, col = col_clus[as.character(clus.labels)],
     main = 'MDS W, color = published clusters', pch = 20,
     xlab = 'Component1', ylab = 'Component2')
```

```{r}
palDF <- ceObj@clusterLegend[[1]]
pal <- palDF[, 'color']
names(pal) <- palDF[, 'name']
plot(fit$points, col = pal[primaryClusterNamed(ceObj)],
     main = 'MDS W, color = our clusters', pch = 20,
     xlab = 'Component1', ylab = 'Component2')
```

```{r}
table(data.frame(published = clus.labels,
                 ours = primaryCluster(ceObj)))
```

@@

```{r}
sampleData <- data.frame(ours = primaryCluster(ceObj))

plotHeatmap(assays(se)$normalizedValues,
            main = 'Normalized values, 1000 most variable genes',
            clusterSamplesData = ceObj@dendro_samples,
            sampleData = as.matrix(sampleData))
```

@@

The goal of this section is to see if we need to refit zinbwave when we want to run slingshot. We run slingshot in the supervised and unsupervised mode and we try k=2, k=3, k=4 in W.

@@

```{r}
Kvec <- c(2, 3, 4)
```

@@

```{r slingshot_sup}
for (k in Kvec){
  X <- W[our_cl != "-1", 1:k]

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m8", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

@@

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m8", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

>>>>

```{r rsec_50}
W <- colData(se)[, grepl('^W', colnames(colData(se)))]
W <- as.matrix(W)
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  ceObj <- RSEC(t(W), k0s = 4:15, alphas = c(0.1), betas = 0.8,
                clusterFunction = "hierarchical01", minSizes=1,
                ncores = 7,
                subsampleArgs = list(resamp.num=100,
                                     clusterFunction="kmeans",
                                     clusterArgs=list(nstart=10)),
                seqArgs = list(k.min=3, top.can=5), verbose=TRUE,
                combineProportion = 0.7,
                mergeMethod = "none")
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

```{r examineCombineMany}
plotClusters(ceObj, colPalette = c(bigPalette, rainbow(200)))
```

@@

FP: Elizabeth, we are working with the W here, does the locfdr make sense in this context? I set eval=FALSE in the next chunk to skip the merging step, let me know if you would rather keep using it. And if we want to still use the merging step, would we want to include it in RSEC function arguments instead of separately?

```{r examineMergeClusters,eval=FALSE}
#re-does merging simpling to make plot 
mergeClusters(ceObj, mergeMethod = "locfdr",
              plotInfo = "mergeMethod", cutoff = 0.01)
```

@@

```{r compareClusters}
plot(fit$points, col = col_clus[as.character(clus.labels)],
     main = 'MDS W, color = published clusters', pch = 20,
     xlab = 'Component1', ylab = 'Component2')
legend(x = 'bottomright', legend = unique(names(col_clus)), cex = .5,
       fill = unique(col_clus), title = 'Sample')
```

```{r}
palDF <- ceObj@clusterLegend[[1]]
pal <- palDF[, 'color']
names(pal) <- palDF[, 'name']
plot(fit$points, col = pal[primaryClusterNamed(ceObj)],
     main = 'MDS W, color = our new clusters', pch = 20,
     xlab = 'Component1', ylab = 'Component2')
legend(x = 'bottomright', legend = names(pal), cex = .5,
       fill = pal, title = 'Sample')
```

@@

FP: Elizabeth, I did not find how to define the column annotation track in the plot below to have the same colors as in ceObj@clusterLegend[[1]]. I tried to use arguments annColors and annCol from aheatmap as it is said in plotHeatmap documentation that for signature matrix arguments can be passed to aheatmap. But I got the error "The following arguments to aheatmap cannot be set by the user in plotHeatmap:Rowv,Colv,color,annCol,annColors".

```{r}
sampleData <- data.frame(ours = primaryCluster(ceObj))
plotHeatmap(assays(se)$normalizedValues,
            main = 'Normalized values, 1000 most variable genes',
            clusterSamplesData = ceObj@dendro_samples,
            sampleData = as.matrix(sampleData))
```

@@

```{r}
table(data.frame(published = clus.labels,
                 ours = primaryClusterNamed(ceObj)))
```

Cluster name | Description | Correspondence
-------------|-------------|-----------------
m1 | resting HBC | original 1, 5
m2 | activated HBC | original 5
m3 | GBC / immature neurons / MV 1 | original 2, 3, 11
m4 | Sus | original 4, 7
m5 | new | new
m6 | new | new
m7 | Neuron | original 9, 12
m8 | Immature Neuron | original 10, 14
m9 | Microvillus | original 15
m10 | Immature Neuron | original 14

The goal of this section is to see if we need to refit zinbwave when we want to run slingshot. We run slingshot in the supervised and unsupervised mode and we try k=3, k=4 in W.

@@

```{r}
Kvec <- c(3, 4)
```

@@

```{r slingshot_sup}
# m11 - original 15 - Microvillus
# m7, m8 - original 9, 12 - Neuron
# m4 - original 4, 7 - Sus

for (k in Kvec){
  X <- W[our_cl != "-1", 1:k]

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m11", "m7", "m8", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

@@

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "m1",
                           end.clus = c("m11", "m4"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)
